The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2011-12-07 smurf_paper.tex
define macro \model for displaying model component names

@@

\begin{table}
  \caption{Summary of the model components that can be fit to
    \scuba\ time-series data with SMURF. Only the first group of
    models are typically fit to the data (\texttt{COM}--\texttt{NOI})
    in the indicated order. The remaining models
    (\texttt{DKS}--\texttt{PLN}) have only been included for
    completeness}
  \vspace{0.2cm}
  \centering
  \begin{tabular}{c|l}
    \hline
    Model & Description \\
    \hline
    \texttt{COM} & remove common-mode signal \\
    \texttt{GAI} & common-mode scaled to each bolometer \\
    \texttt{EXT} & extinction correction \\
    \texttt{FLT} & Fourier transform filter \\
    \texttt{AST} & map estimate of astronomical signal \\
    \texttt{NOI} & noise estimation \\
    \hline
    \texttt{DKS} & dark squid cleaning along columns \\
    \texttt{SMO} & time-domain smoothing filter \\
    \texttt{PLN} & 2-dimensional time-varying plane removal \\
    \hline
    \end{tabular}
  \label{tab:components}
\end{table}

\subsubsection{\texttt{COM,GAI}: common-mode estimation}
\label{sec:comgai}

@@

\subsubsection{\texttt{EXT}: extinction correction}
\label{sec:ext}

@@

\subsubsection{\texttt{FLT}: fourier transform filter}
\label{sec:flt}

This model takes the FFT of the bolometer data, and can apply both
high- and low-pass filters, as well as notch filteres, at hard
frequency edges specified by the user. Alternatively, the frequency
edges of the filters may be defined in terms of an \emph{angular
  scale}, but converted into a frequency through knowledge of the mean
telescope slew speed. The time-series may optionally have apodization
applied before the transform to avoid ringing (primarily caused by
wrap-around discontinuities at the ends of the time-series). Finally,
a whitening filter may also be applied in which a simple $1/f^\alpha +
\mathrm{constant}$ is fit to the power spectrum of each bolometer, and
then the bolometer FFT is multiplied by its inverse (though normalized
to preserve the white noise level).  The signal that is \emph{removed}
from the time-series by this process are stored in the \texttt{FLT}
container array.

\subsubsection{\texttt{AST}: map estimation}
\label{sec:ast}

@@

In addition to map estimation, the \texttt{AST} model can also be used
to perform map-based despiking of the time-series
(Section~\ref{sec:mapdespike}), and to apply constraints to the map to
improve convergences (Section~???).

\subsubsection{\texttt{NOI}: noise estimation}
\label{sec:noi}

The primary purpose of the noise component, \texttt{NOI} is to measure
the noise in each bolometer residual once all of the other models have
been fit and removed. This noise may then be used to estimate weights
for the data in subsequent iterations.

@@

Since noise estimation is usually calculated as the final step, it is
the cleanest data for which some cleaning operations may be
performed. For this reason \texttt{NOI} can optionally use the
time-domain DC step fixer (Section~\ref{sec:steps}) and spike
detection (Section~\ref{sec:timedespike}).

\subsubsection{\texttt{DKS}: dark squid cleaning along columns}
\label{sec:dks}

Columns share significant magnetic field pickup which is measured by
the dark squids. This model has been included although it makes little
improvement, or injects noise since the magnetic field pickup noise is
generally sub-dominant. Furthermore, not every column that contains
working bolometers also has a working dark squid. An alternative is to
use the \texttt{TMP} model described below.

@@

\subsubsection{\texttt{TMP}: remove a scaled template}

Since the \texttt{DKS} cannot generally be used due to the missing
dark squids, an alternative is to use the telescope pointing as a
proxy for the signal due to magnetic field pickup
(Section~\ref{sec:magpickup}. Generally speaking the azimuth (or its
sine) as a function of time is used as a template that is simply
scaled and removed from each bolometer signal. Some modest
improvements can be achieved with this model.

\subsubsection{\texttt{SMO}: time-domain smoothing filter}
\label{sec:smo}

@@

\subsubsection{\texttt{PLN}: 2d time-varying sky noise plane removal}
\label{sec:pln}

>>>>

% how are model names displayed
\newcommand{\model}[1]{\texttt{#1}}

@@

\begin{table}
  \caption{Summary of the model components that can be fit to
    \scuba\ time-series data with SMURF. Only the first group of
    models are typically fit to the data (\model{COM}--\model{NOI})
    in the indicated order. The remaining models
    (\model{DKS}--\model{PLN}) have only been included for
    completeness}
  \vspace{0.2cm}
  \centering
  \begin{tabular}{c|l}
    \hline
    Model & Description \\
    \hline
    \model{COM} & remove common-mode signal \\
    \model{GAI} & common-mode scaled to each bolometer \\
    \model{EXT} & extinction correction \\
    \model{FLT} & Fourier transform filter \\
    \model{AST} & map estimate of astronomical signal \\
    \model{NOI} & noise estimation \\
    \hline
    \model{DKS} & dark squid cleaning along columns \\
    \model{SMO} & time-domain smoothing filter \\
    \model{PLN} & 2-dimensional time-varying plane removal \\
    \hline
    \end{tabular}
  \label{tab:components}
\end{table}

\subsubsection{\model{COM,GAI}: common-mode estimation}
\label{sec:comgai}

@@

\subsubsection{\model{EXT}: extinction correction}
\label{sec:ext}

@@

\subsubsection{\model{FLT}: fourier transform filter}
\label{sec:flt}

This model takes the FFT of the bolometer data, and can apply both
high- and low-pass filters, as well as notch filteres, at hard
frequency edges specified by the user. Alternatively, the frequency
edges of the filters may be defined in terms of an \emph{angular
  scale}, but converted into a frequency through knowledge of the mean
telescope slew speed. The time-series may optionally have apodization
applied before the transform to avoid ringing (primarily caused by
wrap-around discontinuities at the ends of the time-series). Finally,
a whitening filter may also be applied in which a simple $1/f^\alpha +
\mathrm{constant}$ is fit to the power spectrum of each bolometer, and
then the bolometer FFT is multiplied by its inverse (though normalized
to preserve the white noise level).  The signal that is \emph{removed}
from the time-series by this process are stored in the \model{FLT}
container array.

\subsubsection{\model{AST}: map estimation}
\label{sec:ast}

@@

In addition to map estimation, the \model{AST} model can also be used
to perform map-based despiking of the time-series
(Section~\ref{sec:mapdespike}), and to apply constraints to the map to
improve convergences (Section~???).

\subsubsection{\model{NOI}: noise estimation}
\label{sec:noi}

The primary purpose of the noise component, \model{NOI} is to measure
the noise in each bolometer residual once all of the other models have
been fit and removed. This noise may then be used to estimate weights
for the data in subsequent iterations.

@@

Since noise estimation is usually calculated as the final step, it is
the cleanest data for which some cleaning operations may be
performed. For this reason \model{NOI} can optionally use the
time-domain DC step fixer (Section~\ref{sec:steps}) and spike
detection (Section~\ref{sec:timedespike}).

\subsubsection{\model{DKS}: dark squid cleaning along columns}
\label{sec:dks}

Columns share significant magnetic field pickup which is measured by
the dark squids. This model has been included although it makes little
improvement, or injects noise since the magnetic field pickup noise is
generally sub-dominant. Furthermore, not every column that contains
working bolometers also has a working dark squid. An alternative is to
use the \model{TMP} model described below.

@@

\subsubsection{\model{TMP}: remove a scaled template}

Since the \model{DKS} cannot generally be used due to the missing
dark squids, an alternative is to use the telescope pointing as a
proxy for the signal due to magnetic field pickup
(Section~\ref{sec:magpickup}. Generally speaking the azimuth (or its
sine) as a function of time is used as a template that is simply
scaled and removed from each bolometer signal. Some modest
improvements can be achieved with this model.

\subsubsection{\model{SMO}: time-domain smoothing filter}
\label{sec:smo}

@@

\subsubsection{\model{PLN}: 2d time-varying sky noise plane removal}
\label{sec:pln}
